%*******************************************************
% Acknowledgements
%*******************************************************
\refstepcounter{dummy}
\cleardoublepage
\pdfbookmark[1]{Acknowledgements}{acknowledgements}

\begin{flushright}{\slshape
    Being taken seriously means missing out on the chance \\
    to be frivolous, promiscuous, and irrelevant. \\
    The desire to be taken seriously is precisely what compels people \\
    to follow the tried and true paths of knowledge production \\
    around which I would like to map a few detours.} \\ \medskip
    --- J. Jack Halberstam, \emph{The Queer Art of Failure}
\end{flushright}



\bigskip

\begingroup
\let\clearpage\relax
\let\cleardoublepage\relax
\let\cleardoublepage\relax
\chapter*{Acknowledgements}
First and foremost, I would like to thank Dr. Dirk Tiede for supportive and attentive supervision, insightful discussions, constructive feedback, patience and unprecedented support -- more generally, for believing in the people he works with and being driven by a much larger vision.

Martin Sudmanns, for his input and direction, both in shaping the topic of this work, but also for technical advice, resources, support and friendship -- I cannot wait to witness what you will accomplish in the years to come.

Andrea Baraldi, for sharing his knowledge and wisdom, and for generously allowing access to and use of part of his life's work.

I would like to thank the other members of the SemEO team, Dr. Stefan Lang and Christian Werner, for valuable input, as well as the rest of the Z\_GIS team for constructive discussions over the past many months, especially Thomas Strasser and Barbara Riedler.

The GIStammtisch crew in Salzburg, for celebrating all of the victories (especially the not so victorious) but also, and perhaps more importantly, commemorating failures.

"Broomhildas", for their tenacious drive to keep improving and for getting back up, especially when we fall together.

My simultaneous sidekick and hero, for being grounded, and, in moments when it seems the sky is falling, reminding me to look up.

Finally, my parents, for all of their unconditional love and support, including my decision not to return to the place I grew-up.

\endgroup
